Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-14 paper.tex
Simplify wording
Remove last paragraph in first section of intro since information existed elsewhere

Vertical-axis wind turbine array field experiments have revealed that
accelerated wake recovery allows for closer spacing when compared with
conventional axial-flow propeller-type turbines \cite{Dabiri2011, Kinzel2012}.
It was observed experimentally that a high solidity vertical-axis cross-flow
turbine's near-wake produces a unique vertical mean velocity field---generated
by blade tip vortex shedding---the advection by which is the largest contributor
to streamwise momentum and energy transport or recovery \cite{Bachant2015-JoT}.
In this study we seek to replicate those same momentum and energy balance
considerations at multiple Reynolds numbers, to examine the implications on how
small scale, i.e. low Reynolds number experiments may be used to study flows in
turbine arrays.

The Reynolds number effects on the maximum performance and 2-D near-wake
profiles of the University of New Hampshire's Reference Vertical Axis Turbine
(UNH-RVAT) were presented in \cite{Bachant2014}. Here we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

@@

In this study we are using a simple cross-flow turbine constructed from
hydrofoils, i.e., the turbine is a lift-driven device in contrast to
drag-driven. A logical starting point for understanding the effects of $Re$ on
overall turbine loading is to first consider simplified cases of individual
foils, and their static and dynamic loading.

>>>>

Vertical-axis wind turbine array field experiments have revealed that
accelerated wake recovery allows for closer spacing when compared with
conventional axial-flow propeller-type turbines \cite{Dabiri2011, Kinzel2012}.
It was observed experimentally that a high solidity vertical-axis cross-flow
turbine's near-wake produces a unique vertical mean velocity field---generated
by blade tip vortex shedding---the advection by which is the largest contributor
to streamwise momentum and energy transport or recovery \cite{Bachant2015-JoT}.
In this study we seek to replicate those same momentum and energy balance
considerations at multiple Reynolds numbers, to examine the implications on how
small scale, i.e., low Reynolds number experiments may be used to study flows in
turbine arrays.

@@

In this study we are using a simple cross-flow turbine constructed from
hydrofoils, i.e., the rotor is lift-driven in contrast to drag-driven. A logical
starting point for understanding the effects of $Re$ on overall turbine loading
is to first consider simplified cases of individual foils, and their static and
dynamic loading.
